Adaptive broadcast tree for multicores

### 2013-04-29 paper.tex
Update of description for link characteristics

\begin{description}
\item[latency] (quantitative) between each pair of nodes (per-edge)
\item[breakdown] (quantitative) of message send cost: Ethernet has
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node)
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): Ethernet is not reliable,
  multicore interconnect networks often are
\item[Security] \& and failure detection (and the cost for that)
\end{description}

>>>>

\begin{description}
\item[latency] (quantitative) between each pair of nodes (per-edge)
\item[breakdown] (quantitative) of message send cost:
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node)
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): 
  multicore interconnect networks often are
%\item[Security] \& and failure detection (and the cost for that)
\end{description}
